Nice layout for comparison of categorical outcomes

### 2024-07-03 text/21/glm-diagnostics.Rmd
Moved pending files

---
title: "Diagnostics for a generalized linear model"
author: "Steve Simon"
source: new
date: "2021-10-18"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Diagnostics for a generalized linear model"
author: "Steve Simon"
source: new
date: "2021-10-18"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
page_update: complete
---

### 2024-07-03 text/24/nice-layout.Rmd
Moved pending files

While it is easy to get R to produce descriptive statistics for categorical outcomes in a research study, it is a bit harder to get R to produce a layout that is publication-ready. Hard, but not impossible. Here is a simple example.Here is a brief abstract.

@@

```{r}
library(kableExtra)
tab07 %>%
  pack_rows("Sex", 1, 2) -> tab08
tab08
```

@@

>>>>

While it is easy to get R to produce descriptive statistics for categorical outcomes in a research study, it is a bit harder to get R to produce a layout that is publication-ready. Hard, but not impossible. Here is a simple example.

@@

```{r}
library(kableExtra)
tab06 %>%
  set_names(c(" ", "Deaths", "Survivors")) %>%
  kbl %>%
  kable_paper(
    "striped", 
    full_width=FALSE) %>%
  pack_rows("Sex", 1, 2) -> tab08
tab08
```

@@

Here is what the code would look like if you used sprintf instead of glue.
